The Promise that R makes

### 2019-03-09 report/report.Rmd
Merge analyses promise_use_and_action and promises for efficiency
Add analyses for arguments and promises

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_distribution_by_type")
```

```{r echo = FALSE}
show_table("argument_distribution_by_type")
```

```{r echo = FALSE, out.width="1000px"}         
show_graph("argument_distribution_by_dot_dot_dot")
```

```{r echo = FALSE}         
show_table("argument_distribution_by_dot_dot_dot")
```

```{r echo = FALSE, out.width="1000px"}         
show_graph("argument_promise_distribution_by_nature")
```

```{r echo = FALSE}         
show_table("argument_promise_distribution_by_nature")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_distribution_by_sharing")
```

```{r echo = FALSE}
show_table("argument_promise_distribution_by_sharing")
```

@@

>>>>

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_count_by_type")
```

```{r echo = FALSE}
show_table("argument_count_by_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("non_missing_argument_count_by_dot_dot_dot")
```

```{r echo = FALSE}
show_table("non_missing_argument_count_by_dot_dot_dot")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_nature")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_nature")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_sharing")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_sharing")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_expression_type")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_expression_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_value_type")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_force_type")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_force_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_direct_lookup_count")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_direct_lookup_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_direct_and_indirect_lookup_count")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_direct_and_indirect_lookup_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_direct_metaprogram_count")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_direct_metaprogram_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_direct_and_indirect_metaprogram_count")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_direct_and_indirect_metaprogram_count")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("promise_argument_count_by_dispatch_type")
```

```{r echo = FALSE}
show_table("promise_argument_count_by_dispatch_type")
```

```{r echo = FALSE}
show_table("promise_argument_forced_by_promise_argument")
```

```{r echo = FALSE}
show_table("promise_argument_returning_non_locally")
```

@@

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_call_depth")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_call_depth")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_promise_depth")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_promise_depth")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("argument_promise_count_by_nested_promise_depth")
```

```{r echo = FALSE}
show_table("argument_promise_count_by_nested_promise_depth")
```
